Approximating the matrix exponential derivative of the CTMC generator matrix, with application to global SARS-CoV-2

### 2023-03-13 manuscript/main.tex
fixed effects
figures done for now
started writing

\title{Approximating the matrix exponential derivative with respect to the CTMC generator matrix, with application to global SARS-CoV-2}

@@

>>>>

\title{Approximating the matrix exponential derivative of the CTMC generator matrix, with application to global SARS-CoV-2}

@@

\begin{figure}[!p]
	\centering
	\includegraphics[width=\linewidth]{fixedEffects.pdf}
	\caption{Fixed effects.}\label{fig:FE}
\end{figure}

\begin{figure}[!p]
	\centering
	\includegraphics[width=\linewidth]{postViz.pdf}
	\caption{Posteriors.}\label{fig:FE}
\end{figure}

Hamiltonian Monte Carlo \citep{neal2011mcmc} is an advanced MCMC procedure that uses numerical approximations to Hamiltonian trajectories to generate proposals far away from the current Markov chain state.  On the one hand, this approach to proposal generation helps reduce autocorrelation between chain states and is particularly helpful within higher-dimensional state spaces.  On the other hand, the numerical integration of Hamilton's equations requires repeated evaluation of the Hamiltonian potential energy's gradient, and these repeated floating-point operations may become computationally burdensome.
